% Book wrote by Miguel Vicente Mesquita/SufremOak
% i wrote this whole book using the overleaf latex guide

\documentclass{book}
\usepackage{amssymb}
% \usepackage{graphicx}
\usepackage{amsmath}
\usepackage{listings}
% \graphicspath{{images/}} % Configuring the graphicx package
\title{The MathAsScripting Book}
\author{Miguel Vicente Mesquita}
\date{April 2024}
\begin{document}

\newpage

\chapter{First Chapter}

\section{Introduction}

\paragraph{What it is?}
MathAsScripting is a solo project made by Miguel V. Mesquita to make math more
like a programming language, like python or crystal in the DeclMath case

\paragraph{But why?}
``I made it to add more sense to math, because all the formulas and other things don't get into my mind''

\paragraph{Understanding the concepts}
All this MathAsScripting project envolves itself at a unic mathematical function:
$$
\{ \sum \longleftrightarrow \varDelta² \} 
$$
This function isn't a common math function, it is a Declarative-Mathetical-Oriented-Function, or DMOF,
DMOF functions are constant based operations that changes a variable contantly in a period of ticks,
which can be metered in computer bits (sequences of 0s and 1s, or binary), in a 8-bit format.

DMOF commonly uses simuntaneous symbols like:
$$
\Longleftrightarrow \longleftrightarrow \leftrightarrow \Leftrightarrow \Updownarrow \updownarrow \nleftrightarrow \nLeftrightarrow
$$
which can create and change constants

by doing
$$
\mathbf{A} \neq \sqrt{200} \div \tan{6}
$$
you will get
$$
\mathbf{A} = \exp \leftrightsquigarrow \mathcal{E}
$$
Which is
$$
\mathbf{A} = \mathbf{10} 
$$
Confusing? Of course, but it is necessary to understand DeclMath.

    \section{Starting with DeclMath}
    DeclMath is an math-based language (obviously) and also an Declarative language,
    as with its looks, it is an DSL language for math purposes, with scientific features
    and some phisics features, and also Mind-based (can "run" on your mind).
    \paragraph{}
    Starting with it is a really simple task, and if you want to make a "hello world"
    with it, good luck, because it is a bit harder than you can think, that language isn't
    made for printing common ASCII characters like Aa-Zz, it is only expression powered,
    which means you can only do mathematical operations and some other things, but a hello world
    isn't a easy task without using any generators, like the Markin Programming language generator
    script.
    \paragraph{}
    To make a "hello, world" operand you will need to get a binary value for it
    so:
    Letter H:
    $$
    \mathbf{H} = \mathbf{7.2 \times 10^1}
    $$
Letter E: 
    $$
    \mathbf{E} = \mathbf{1.000101 \times 10^8}
    $$
Letter L:
$$
\mathbf{L} = \mathbf{1.0011 \times 10^6}
$$
Letter O: 
$$
\mathbf{O} = \mathbf{7.2 \times 10^1}
$$
Here is an implementation in DeclMath:

    \begin{lstlisting}
        #lang 'en'

        # map the ascii characters
        h = expr(7.2&.&10^1);
        e = expr(1.00010&.&10^8)
        l = expr(1.0011&.&10^6)
        o = expr(7.2&.&10^1^2)

        f(get h, e, l, o):
            for \n in 5:
                show(h)
                show(e)
                show(l) in 2^1
                show(o) 
    \end{lstlisting}

    that will output:
        \begin{lstlisting}
            hello
        \end{lstlisting}

    you probably noticed those strange expressions:
    \begin{lstlisting}
        h = expr(7.2&.&10^1);
        e = expr(1.00010&.&10^8)
        l = expr(1.0011&.&10^6)
        o = expr(7.2&.&10^1^2)
    \end{lstlisting}

    those are the binary code of the ASCII letters "H", "E", "L" and "O"
    in scientific notation, which is the only method of binary input in DeclMath.

    \section{Math functions}

    Now we're diving into Math functions, which you most know as $\DeclareMathOperator{f}{(x)}$ or $\DeclareMathOperator{g}{(x)}$.
    \subsection{Using Math functions in DeclMath.}
    DeclMath uses common math functions, but in a unformatted form, like just f(x) or g(x).
    An function uses the following logic:

    $$
    \mathbf{x} = \sqrt{\DeclareMathOperator{f}{(T^3)}}
    $$
    $$
    \mathbf{T} = [ \Delta + \mathbf{Fz} ]
    $$
    Which will get the values from $\mathbf{T^3}$ and read and change it's values constantly, like a constant, but it can be readed by a function using $\DeclareMathOperator{f}{(x)}$.
    

\end{document}
